|

### 2020-01-11 nontex/install/windows/fn_installations.Rmd
atom cson, vscode zen mode no minimap

- Zen model: *Ctrl + k, z*, this means press control k, then press z
- Open up Settings: *Ctrl + ,*
- Preview Markdown in VSCode: *Ctrl + Shift + v*
- Open up left pane: *Ctrl + b*
- Wrap Text: *alt + z*, switch between wrap or not to save screen space for example.
- Hide Console Pane (running code): *Ctrl + j*

@@

```
# https://github.com/t9md/atom-vim-mode-plus/issues/130
'atom-text-editor.vim-mode-plus.insert-mode':
  'j j': 'vim-mode-plus:activate-normal-mode'
```

>>>>

- see all shortcuts: *Ctrl + k, ctrl + s*
- Zen model: *Ctrl + k, z*, this means press control k, then press z
    + note that z mode can be adjusted by shiftin the bar on the left
- Open up Settings: *Ctrl + ,*
- Preview Markdown in VSCode: *Ctrl + Shift + v*
- Open up left pane: *Ctrl + b*
- Wrap Text: *alt + z*, switch between wrap or not to save screen space for example.
- Hide Console Pane (running code): *Ctrl + j*

*personal bindings*

- toggle minimap: *Ctrl + k, ctrl + z*

@@

```
'atom-text-editor':
  'ctrl-shift-j': 'pretty-json:prettify'
  'alt-z':'date:date'
  'alt-x':'date:time'
  'alt-c':'date:datetime'
'body':
  'ctrl-tab': 'pane:show-next-item'
  'ctrl-shift-tab': 'pane:show-previous-item'
'.editor':
  'ctrl-alt-z': 'atom-beautify:beautify-editor'
  'ctrl-shift-r': 'hydrogen:restart-kernel'
'atom-text-editor:not([mini])':
  'ctrl-*': 'highlight-selected:select-all'
'atom-text-editor, webview.markdown-preview-plus':
  'ctrl-shift-X': 'markdown-preview-plus:toggle-render-latex'

# https://github.com/t9md/atom-vim-mode-plus/issues/130
'atom-text-editor.vim-mode-plus.insert-mode':
  'j j': 'vim-mode-plus:activate-normal-mode'
```
